### 2018-05-07 introduction/intro.tex
Clean up Intro/Formatting

The primary downside of wide-field searches is that they must contend with the challenge of ruling out false positives that arise from unrelated contaminating transients \citep{CowpBerger15}. Observing even $\apx100$~deg$^2$ of sky over the course of a night will reveal numerous new transients of both galactic and extragalactic origin. While the rates of these contaminants are expected to be low \citep[$\mathcal{R} \apx 2$ events per deg$^2$][]{Cowp+17}, they still present a challenge when trying to identify the presence of a genuine EM counterpart in the data. The other major challenge facing wide-field searches is simply observing time available \citep{CowpBerger15}. It may not be possible to observe an entire localization in a single night of observing leading to uneven cadence and coverage which will weaken the analysis.

>>>>

The primary downside of wide-field searches is that they must contend with the challenge of ruling out false positives that arise from unrelated contaminating transients \citep{CowpBerger15}. Observing even $\apx100$~deg$^2$ of sky over the course of a night will reveal numerous new transients of both galactic and extragalactic origin. While the rates of these contaminants are expected to be low \citep[$\mathcal{R} \apx 2$ events per deg$^2$][]{Cowp+17b}, they still present a challenge when trying to identify the presence of a genuine EM counterpart in the data. The other major challenge facing wide-field searches is simply observing time available \citep{CowpBerger15}. It may not be possible to observe an entire localization in a single night of observing leading to uneven cadence and coverage which will weaken the analysis.
